Project 1 of Deep Learning\\ \textit{\Large{Classification, weight sharing, auxiliary losses}}

### 2019-05-16 report-latex/paper.tex
added latex report

\begin{abstract}
The aim of this project was to show the impact of weight sharing and the use of an auxiliary loss. The task was to compare two digits represented as a two-channel image. We have started experimenting with a linear model and, then, we have implemented more complex non-linear and convolutional models. Our experiments show that, indeed, the use of weight sharing, i.e. convolutional layers, and the use of two losses leads to the best solution in his classification problem, achieving an error rate slightly higher than 15\%.
\end{abstract}

@@

Section \ref{sec:data} explains the structure of the dataset, Section \ref{sec:codestruc} describes briefly the content of each file. Section \ref{sec:auxilaryloss} explain which auxiliary loss we have used. In Section \ref{sec:comparison} and \ref{sec:conclusion} we have showed the performance accuracy obtained by each model using a cross validation, explaining why we got these results.

\section{Data}
\label{sec:data}
Both the train and the test sets consist of $1000$ samples. Each input sample is a tensor of shape $2\times14\times14$ tensor and represents 2 images in grayscale. While each target sample is represented by 2 tensors: (1) a single value tensor representing the boolean prediction (greater than), and (2) a two values tensor representing the classes of the two digits. The MNIST data set is made of handwritten digits (from $0$ to $9$); to load the dataset we have used the provided function \texttt{generate\_pair\_sets(N)}.

\section{Code structure}
\label{sec:codestruc}
This section describes the content of each file.
\begin{itemize}
    \item \texttt{code/data.py}: class to generate the dataset. Contains different methods (e.g. flat the input, get a dataset in 2D or in 3D, enable the hot-encoding).
    \item \texttt{code/model.py}: general class to define a model to train and test it (with corresponding plot and history).
    \item \texttt{code/models\_implemented.py}: contains all the model classes (e.g. NNModel1Loss, CNNModel2Loss).
    \item \texttt{main.py}: contains examples of each model, in order to call and train it.
\end{itemize}
Files \texttt{code/cross\_validation\_report.py} and \texttt{BoxPlot\_generator.ipynb} are made for report purposes.

@@

\section{Conclusion}
\label{sec:conclusion}
Convolutional Neural Network represents the best model with images recognition. Moreover, the CNN with 2 losses seems to perform slightly better since it learned to extract high-lever feature representing the two digits. We have seen that weight sharing (CNN) improves the accuracy and the robustness of the model, the use of an auxiliary loss in this context improves the obtained results. Our implementation of CNN takes around $190$ seconds, the architecture that we have implemented requires \texttt{conv3d} and \texttt{batchnorm3d} that maybe are not optimized for CPU. In the \texttt{main.py} we implemented the same architecture but using only 2D convolutions, this implementation requires around $160$ seconds.

>>>>

\begin{abstract}
The aim of this project was to show the impact of weight sharing and the use of an auxiliary loss. The task was to compare two digits represented as a two-channel image. We have started experimenting with a linear model and, then, we have implemented more complex non-linear and convolutional models. Our experiments show that, indeed, the use of weight sharing, i.e. convolutional layers, and the use of two losses leads to the best solution in his classification problem, achieving an error rate around 15\%.
\end{abstract}

@@

Section \ref{sec:data} explains the structure of the dataset, Section \ref{sec:codestruc} describes briefly the content of each file. In Section \ref{sec:comparison} and \ref{sec:conclusion} we have showed the performance accuracy obtained by each model using a cross validation, explaining why we got these results.

\section{Data}
\label{sec:data}
Both the train and the test sets consist of $1000$ samples. Each input sample is a tensor of shape $2\times14\times14$ tensor and represents 2 images in grayscale. While each target sample is represented by 2 tensors: (1) a single value tensor representing the boolean prediction (greater than), and (2) a two values tensor representing the classes of the two digits. The MNIST data set is made of handwritten digits (from $0$ to $9$); to load the dataset we have used the provided function \texttt{generate\_pair\_sets(N)} in file \texttt{dlc\_practical\_prologue.py}.

\section{Code structure}
\label{sec:codestruc}
This section describes the content of each file.
\begin{itemize}
    \item \texttt{code/data.py}: class to generate the dataset. Contains different methods (e.g. flat the input, get a dataset in 2D or in 3D, enable the hot-encoding).
    \item \texttt{code/model.py}: general class to define a model to train and test it (with corresponding plot and history).
    \item \texttt{code/models\_implemented.py}: contains all the model classes (e.g. NNModel1Loss, CNNModel2Loss).
    \item \texttt{main.py}: contains examples of each model, in order to call and train it.
\end{itemize}
Files \texttt{cross\_validation\_report.py} and \texttt{BoxPlot\_generator.ipynb} are made for report purposes.

@@

\section{Conclusion}
\label{sec:conclusion}
Convolutional Neural Network represents the best model with images recognition. Moreover, the CNN with 2 losses seems to perform slightly better since it learned to extract high-lever feature representing the two digits. We have seen that weight sharing (CNN) improves the accuracy and the robustness of the model, the use of an auxiliary loss in this context improves the obtained results. Our implementation of CNN takes around $190$ seconds, the architecture that we have implemented requires \texttt{conv3d} and \texttt{batchnorm3d} that maybe are not optimized for CPU. In the \texttt{models\_implemented.py} we implemented the same architecture but using only 2D convolutions, this implementation requires around $160$ seconds.
